Compositional equivalences based on Open pNets

### 2020-02-04 2016-Weak-FH-Bisim/WeakBisim.tex
nearly finished Fig 7
+1

\TODO{Eric: insert here a table with the details of the WOTs.Il manque encore au moins 3 WOT dans ce dessin...}

\smallskip
$1^st$ try, user-friendly style:

$$ 3 = \tau^*; \underline{in(m)}\{s1\_c:=0, s1\_m:=m\}; \tau\{s1\_c++\}^*$$

\smallskip
$2^nd$ try, full formal style ?:
\medskip

@@

Then the effect of one single $100 -> 210 -> 220 -> 100$ loop as:
\smallskip

$Post_{456} = post_6\shortotimes post_5\shortotimes post_4$
\medskip

And we can now define the weak OTs:
\smallskip

@@

$ 3 = \openrule
         {\{P\mapsto p\_send(m)\}, True, post_4\shortotimes {Post_{456}}^*\shortotimes\ post_3}
         {000 \OTWeakarrow {\texttt{in(m)}} 100}$

>>>>

\TODO{Define $\tau = \openrule{\{\}, True, ()}{xxx \OTWeakarrow {\tau} xxx}$}

\TODO{Define *}

% \TODO{Eric: insert here a table with the details of the WOTs.Il manque encore au moins 3 WOT dans ce dessin...}

% \smallskip
% $1^st$ try, user-friendly style:

% $$ 3 = \tau^*; \underline{in(m)}\{s1\_c:=0, s1\_m:=m\}; \tau\{s1\_c++\}^*$$

%\smallskip
%$2^nd$ try, full formal style ?:
%\medskip

@@

Then the effect of one single $100 \rightarrow{4} 210 \rightarrow{5} 220 \rightarrow{6} 100$ loop as:
\smallskip

$Post_{456} = post_6\shortotimes post_5\shortotimes post_4$, that can be simplified as: $(s1\_c\gets s1\_c+1)$
\medskip

Iterating as: ${Post_{456}}^*$ =  $(s1\_c\gets s1\_c+n)$ for some $n\ge 0$
\medskip

Finaly WOT 3 has a substitution $\shortotimes {Post_{456}}^*\shortotimes\ post_3$ = $(s1\_c\gets 0+n)$
\medskip

and WOT 3' has $post_4\shortotimes {Post_{456}}^*\shortotimes\ post_3$
= $(m1\_msg\gets m, m1\_c\gets 0+n)$
\medskip

We can now define the weak OTs:
\smallskip

@@

$ 3 = \openrule
         {\{P\mapsto p\_send(m)\}, True, {Post_{456}}^*\shortotimes\ post_3}
         {000 \OTWeakarrow {\texttt{in(m)}} 100}$

$ 3' = \openrule
         {\{P\mapsto p\_send(m)\}, True, post_4\shortotimes {Post_{456}}^*\shortotimes\ post_3}
         {000 \OTWeakarrow {\texttt{in(m)}} 210}$
